The rough Bergomi (rBergomi) model, introduced recently in  \cite{bayer2016pricing}, is a promising rough volatility model in quantitative finance. This new model exhibits consistent results with the empirical fact of implied volatility surfaces being essentially time-invariant. This model also has  the  ability to capture the term structure of skew observed in equity markets. In the absence of analytical European option pricing methods for the model, and due to the non-Markovian nature of the fractional driver, the prevalent option is to use Monte Carlo (MC) simulation for pricing. Despite recent advances in the MC method in this context, pricing under the rBergomi model is still a time-consuming task. To overcome this issue, we design a novel,  alternative, hierarchical approach, based on adaptive sparse grids quadrature \red{(ASGQ)}, specifically using the same construction in \cite{haji2016multi}, coupled with Brownian bridge construction and Richardson extrapolation. By uncovering the available regularity,  our hierarchical method demonstrates substantial computational gains with respect to the standard MC method, when reaching a sufficiently small error tolerance in the price estimates across different parameter constellations, even for very small values of the Hurst  parameter. Our work opens a new research direction in this field, i.e. to investigate the performance of  methods  other than Monte Carlo for pricing and calibrating under the rBergomi model.

\

\textbf{Keywords} Rough volatility, Monte Carlo, Adaptive sparse grids, Brownian bridge construction, Richardson extrapolation.

\textbf{2010 Mathematics Subject Classification} 	91G60, 	91G20, 65C05, 65D30, 65D32.