\documentclass[11pt]{article}

%\usepackage{setspace}
%\documentclass[final,leqno]{siamltex}
\usepackage{smoothing_paper}



\usepackage[section]{placeins}
\usepackage{tabularx,ragged2e,booktabs,caption}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%chiheb commands

\interfootnotelinepenalty=10000
%%%%%%%%%%%%%%%%%
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\cf}{\emph{cf.}}
\newcommand{\prob}[1]{\mathrm{P}\left(#1\right)}
\newcommand{\expt}[1]{\mathrm{E}\left[#1\right]}
\newcommand{\expth}[1]{\hat{\mathrm{E}}\left[#1\right]}



\newcommand{\rset}{\mathbb{R}}
\newcommand{\nset}{\mathbb{N}}
\newcommand{\zset}{\mathbb{Z}}



\newcommand{\PERIOD}{.}
\newcommand{\COMMA}{,}
\newcommand{\BIGSPACE}{\,\,\,\,\,\,\,}



\newcommand{\Ordo}[1]{{\mathcal{O}}\left(#1\right)}
\newcommand{\ordo}[1]{{o}\left(#1\right)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% DO WE RELLY NEED THE FOLLOWING??

%%  new margin
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{plain}                                                      %%
%%%%%%%%%% EXACT 1in MARGINS %%%%%%%                                   %%
\setlength{\textwidth}{6.5in}     %%                                   %%
\setlength{\oddsidemargin}{0in}   %%   
\setlength{\evensidemargin}{0in}  %%        
\setlength{\textheight}{8.5in}    %%       
\setlength{\topmargin}{-0.2in}    %%   
\setlength{\headheight}{0in}      %%    
\setlength{\headsep}{0in}         %%                   
\setlength{\footskip}{.5in}       %%                       
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                   %%
\newcommand{\required}[1]{\section*{\hfil #1\hfil}}                    %%
\renewcommand{\refname}{\hfil References Cited\hfil}                   %%

\def\SMALLSKIP{\smallskip}
\def\MEDSKIP{\medskip}
\def\BIGSKIP{\bigskip}

%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Hierarchical adaptive sparse  grids for option pricing under the rough Bergomi model} 



\author{Christian Bayer\thanks{
 Weierstrass Institute for Applied Analysis and Stochastics (WIAS),
 Berlin, Germany.}
        \and Chiheb Ben Hammouda\thanks{King Abdullah University of Science and Technology (KAUST), Computer, Electrical and Mathematical Sciences \& Engineering Division (CEMSE), Thuwal $23955-6900$, Saudi Arabia ({\tt chiheb.benhammouda@kaust.edu.sa}).} 
\and  Raul Tempone\thanks{King Abdullah University of Science and Technology (KAUST), Computer, Electrical and Mathematical Sciences \& Engineering Division (CEMSE), Thuwal $23955-6900$, Saudi Arabia ({\tt raul.tempone@kaust.edu.sa}).} \thanks{Alexander von Humboldt Professor in Mathematics for Uncertainty Quantification, RWTH Aachen University, Germany.}}

%\doublespacing
\begin{document}
\maketitle

\begin{abstract}
	\input{abstract}  
\end{abstract}






%\pagestyle{myheadings}
\thispagestyle{plain}

\setcounter{tocdepth}{1}


 \section{Introduction}
\input{introduction}



 \section{Problem setting}\label{sec:Problem setting}

\input{problem_setting}

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \section{Weak error discussion and the optimal simulation scheme for our approach}\label{sec:Weak error analysis}

\input{Weak_error_analysis.tex}

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\section{Details of our hierarchical method}\label{sec:Details our approach and error bounds}

\input{our_approach_details}



%\section{Details of Cholesky scheme coupled with hierarchical reresentation}\label{sec:Details of Cholesky scheme coupled with hierarchical reresentation}
%
%\input{Cholesky_hierarchical.tex}


% \section{MISC error estimate}\label{sec:MISC error estimate}
%\input{MISC_error_estimate}

  \section{Numerical experiments}\label{sec:Numerical tests}
\input{numerical_section}



\section{Conclusions and future work}

\input{Conclusion}

\

\textbf{Acknowledgments} C. Bayer gratefully acknowledges support from the German Research Foundation (DFG, grant BA5484/1). This work was supported by the KAUST Office of Sponsored Research (OSR) under Award No. URF/1/2584-01-01 and the Alexander von Humboldt Foundation. C. Ben Hammouda and R. Tempone are members of the KAUST SRI Center for Uncertainty Quantification in Computational Science and Engineering. The authors would like to thank Joakim Beck, Eric Joseph Hall and Erik von Schwerin for their helpful and constructive comments that greatly contributed to improving the final version of the paper. 



 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%References
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{plain}
\bibliography{smoothing_rBergomi.bib} 




%\appendix
%\input{appendix.tex}






 

 

 
 
 


\end{document}